Clustering four designs 500 iter

### 2021-11-07 main.Rmd
files upload

authors:
- name: Sayani Gupta
  affiliation: Department of Econometrics and Business Statistics, Monash University
  thanks: "Email: Sayani.Gupta@monash.edu"

- name: Rob J Hyndman
  affiliation: Department of Econometrics and Business Statistics, Monash University

- name: Dianne Cook
  affiliation: Department of Econometrics and Business Statistics, Monash University

>>>>

authors:
- name: Sayani Gupta
  affiliation: Department of Econometrics and Business Statistics, Monash University
  thanks: "Email: Sayani.Gupta@monash.edu"
- name: Dianne Cook
  affiliation: Department of Econometrics and Business Statistics, Monash University
- name: Rob J Hyndman
  affiliation: Department of Econometrics and Business Statistics, Monash University

### 2021-11-07 paper-supplementary.Rmd
files upload

gran_cat_dist <- data_validation_cat %>% 
  mutate(customer_from = as.character(customer_from),
         customer_to = as.character(customer_to)) %>% 
  left_join(cluster_result, by = c("customer_from" = "customer_id")) %>% 
  rename("group_from" = "group") %>% 
  left_join(cluster_result, by = c("customer_to" = "customer_id")) %>%  
  rename("group_to" = "group") %>% 
  group_by(gran,
           category,
           group_from, 
           group_to) %>% 
  summarise(sum = sum(distance)) %>% 
  pivot_wider(names_from = group_to, values_from = sum) %>% 
  mutate(distance = sum(`1`, `2`, `3`, `4`, `5`,`6`, `7`, `8`, `9`, `10`, `11`, `12`, `13`, `14`, `15`, `16`, `17`)) %>% 
  select(-(4:8)) %>% 
  arrange(-distance)

>>>>

gran_cat_dist_from <- data_validation_cat %>% 
  mutate(customer_from = as.character(customer_from),
         customer_to = as.character(customer_to)) %>% 
  left_join(cluster_result, by = c("customer_from" = "customer_id")) %>% 
  rename("group_from" = "group") %>% 
  left_join(cluster_result, by = c("customer_to" = "customer_id")) %>%  
  rename("group_to" = "group") %>% 
  group_by(gran,
           category,
           group_from, 
           group_to) %>% 
  summarise(sum = sum(distance)) %>% 
  pivot_wider(names_from = group_to, values_from = sum) %>% 
  mutate(distance = sum(`1`, `2`, `3`, `4`, `5`,`6`, `7`, `8`, `9`, `10`, `11`, `12`, `13`, `14`, `15`, `16`, `17`)) %>% 
  select(-(4:8)) %>% 
  arrange(-distance) %>% 
    rename("group"="group_from")

gran_cat_dist_to <- data_validation_cat %>% 
  mutate(customer_from = as.character(customer_from),
         customer_to = as.character(customer_to)) %>% 
  left_join(cluster_result, by = c("customer_from" = "customer_id")) %>% 
  rename("group_from" = "group") %>% 
  left_join(cluster_result, by = c("customer_to" = "customer_id")) %>%  
  rename("group_to" = "group") %>% 
  group_by(gran,
           category,
           group_from, 
           group_to) %>% 
  summarise(sum = sum(distance)) %>% 
  pivot_wider(names_from = group_from, values_from = sum) %>% 
  mutate(distance = sum(`1`, `2`, `3`, `4`, `5`,`6`, `7`, `8`, `9`, `10`, `11`, `12`, `13`, `14`, `15`, `16`, `17`)) %>% 
  select(-(4:8)) %>% 
  arrange(-distance) %>% 
    rename("group"="group_to")

### 2021-11-07 supplementary/algorithm1/real-data/cluster4-iter100.Rmd
files upload

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
read_chunk("R/simdata01.R")
```

>>>>

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
library(here)
read_chunk(here::here("validation/old/simdata01.R"))
```

### 2021-11-07 supplementary/old/cluster4-iter500.Rmd
files upload

---
title: "Clustering four designs"
output:
  bookdown::pdf_book:
    MonashEBSTemplates::workingpaper:
    #base_format: rticles::asa_article
    fig_height: 8
    fig_width: 12
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes
---

@@

```{r, echo=TRUE}
sample_seed <-  seq(10, 100, 10)
```

>>>>

---
title: "Clustering four designs 500 iter"
output:
  bookdown::pdf_book:
    MonashEBSTemplates::workingpaper:
    #base_format: rticles::asa_article
    fig_height: 8
    fig_width: 12
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes
---

@@

```{r, echo=TRUE}
sample_seed <-  seq(1, 500, 1)
```
